estimation of effect sizes and detection of significant effects

### 2017-10-08 analysis/estimation_of_effect_size.Rmd
wflow_publish("estimation_of_effect_size.Rmd")

---
title: "estimation of effect sizes and detection of significant effects"
author: "Zhiwei Ma"
date: YYYY-MM-DD
output: html_document
---

@@

Changing the threshold for lfsr, we plot the ROC curve for $K=1,2,4,10$. Notice that when $K=1$, it is equvalent to apply ash to each study separately, and $K = 4$ is the true model.

>>>>

---
title: "estimation of effect sizes and detection of significant effects"
author: "Zhiwei Ma"
date: 2017-10-08
output: html_document
---

@@

Changing the threshold for lfsr, we plot the ROC curve for $K=1,2,4,10$. Notice that when $K=1$, it is equvalent to applying ash to each study separately, and $K = 4$ is the true model.
